---
title: "Meta-Analysis"
author: "Kavya"
date: "9/20/2020"
output: html_document
---

```{r}
#install.packages("meta")
#install.packages("metafor")
#install.packages("esc")
library(meta)
library(esc)
library(metafor)
#install.packages("QuantPsyc")
library(QuantPsyc)
#install.packages("forestplot")
library(forestplot)
```

https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html

Neurology Paper - We chose a fixed-effects method over a random effects model to avoid exacerbating potential bias due to differences in sample size and available data in the two cohorts. 

I standardized the regressions below - is this the right move? 
Any suggestions on calculating effect size? I calculated using standardized regression coefficients. https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/b.html#b

Also, unsure what to enter for group1 and group2 size as we are not using controls here: just discovery and extension cohorts. I just entered in the ext and disc cohort sizes. 

```{r}
#First we need to randomly split the data into Discovery and Extension
All_msrsr_dem1115 <- rbind(CUIMC_msrsr_median_latest_dem_1115,Pitt_msrsr_median_latest_dem_1115)

# Split MSRSR Data into Training and Testing in R 
sample_size = floor(0.7*nrow(All_msrsr_dem1115))
set.seed(876)
picked = sample(seq_len(nrow(All_msrsr_dem1115)),size = sample_size)
Discovery_msrsr = All_msrsr_dem1115[picked,]
Extension_msrsr = All_msrsr_dem1115[-picked,]

```

```{r}

#msrsr vs depravity correlation for discovery
disc_msrsr_lm <- lm(msrsr_median ~ PC1, Discovery_msrsr)
cor(scale(Discovery_msrsr$msrsr_median), scale(Discovery_msrsr$PC1), method="pearson")
summary(disc_msrsr_lm)
lm.beta(disc_msrsr_lm)

disc_msrsr_lm <- lm(msrsr_median ~ PC1, Discovery_msrsr)
disc_msrsr_lm$vi <- 0
disc.res.rma <- rma(disc_msrsr_lm, vi, mods =  ~ PC1, method = "FE", data=Discovery_msrsr)


#Calculating effect size for Discovery Cohort
esc_beta(beta=0.2316798, sdy=1.946e-02, grp1n=2501, grp2n= 1073, es.type = "g") #unsure of what to put in group1 size and group2 size


ext_msrsr_lm <- lm(scale(msrsr_median) ~ scale(PC1), Extension_msrsr)
cor(scale(Extension_msrsr$msrsr_median), scale(Extension_msrsr$PC1), method = "pearson")
summary(ext_msrsr_lm)
lm.beta(ext_msrsr_lm)

#Calculating effect size for Extension Cohort
esc_beta(beta=0.2068889, sdy=2.990e-02, grp1n=1073, grp2n=2501, es.type = "g") #unsure of what to put in group1 size and group2 size

meta <- fread("meta2.csv")
fixed_meta <- metagen(TE,
             seTE,
             data=meta,
             studlab=paste(cohort),
             comb.fixed = TRUE,
             comb.random = FALSE,
             prediction=TRUE,
             sm="SMD")
fixed_meta

png("forest_fixedmeta_msrsr.png")
forest(fixed_meta, 
       xlim = c(.35, .65),
       leftlabs = c("Cohort", "Beta", "SE"))
dev.off()


metacor <- fread("meta.csv")

m.cor <- metacor(cor, 
                 n, 
                 data = metacor,
                 studlab = metacor$Cohort,
                 sm = "ZCOR",
                 method.tau = "SJ")
forest(m.cor)

png(file = 'forestplot.png') 
forest(m.cor, 
       xlim = c(.1,.3))
dev.off()

```

```{r}
#install.packages("lm.beta")
library(lm.beta)

Pitt_msrsr_covar_1115 <- lm(formula = msrsr_median ~ age_latestPRO + sex + race_ethnicity_combo + age_firstsx + dx_dur_adjust + DMT_Group + PC1, data = Pitt_msrsr_median_latest_dem_1115)

summary(Pitt_msrsr_covar_1115)$coefficients
lm.beta(Pitt_msrsr_covar_1115)
tab_model(Pitt_msrsr_covar_1115)

CUIMC_msrsr_covar_1115 <- lm(formula = msrsr_median ~ age_latestPRO + sex + race_ethnicity_combo + age_firstsx + dx_dur_adjust + DMT_Group + PC1, data = CUIMC_msrsr_median_latest_dem_1115)

summary(CUIMC_msrsr_covar_1115)$coefficients
tab_model(CUIMC_msrsr_covar_1115)
lm.beta(CUIMC_msrsr_covar_1115)

meta_msrsr <- fread("msrsr_meta.csv")

metaanalysis_msrsr <- metagen(TE,
                seTE,
                data=meta_msrsr,
                studlab=paste(Cohort),
                comb.fixed = FALSE,
                comb.random = TRUE,
                hakn = FALSE,
                prediction=TRUE,
                sm="")

metaanalysis_msrsr


svg(file = 'msrsr_metaplot.svg') 
msrsr_metaplot <- forest(metaanalysis_msrsr,
       xlim = c(-1,1),
       col.diamond = "black",
       digits.pval = 4,
       print.I2.ci = FALSE,
       print.tau2 = FALSE,
       pooled.totals = FALSE,
       xlab.pos = 0,
       digits = 3,
       col.predict = "black",
       text.random = "Meta Analysis",
       leftcols = c("studlab", "effect", "ci", "n"), 
       leftlabs = c("Cohort", "Estimate","95%-CI", "N"),
       just = "center", just.addcols = "center", just.studlab = "center",
       rightcols = FALSE
)
dev.off()

```

```{r}

Pitt_promis_covar_1115 <- lm(formula = promis_median ~ age_latestPRO + sex + race_ethnicity_combo + age_firstsx + dx_dur_adjust + DMT_Group + PC1, data = Pitt_promis_median_latest_dem_1115)
summary(Pitt_promis_covar_1115)$coefficients
tab_model(Pitt_promis_covar_1115)

CUIMC_promis_covar_1115 <- lm(formula = promis_median ~ age_latestPRO + sex + race_ethnicity_combo + age_firstsx + dx_dur_adjust + DMT_Group + PC1, data = CUIMC_promis_median_latest_dem_1115)
summary(CUIMC_promis_covar_1115)$coefficients
tab_model(CUIMC_promis_covar_1115)

promis_meta <- fread("meta_promis.csv")


metaanalysis_promis <- metagen(TE,
                seTE,
                data=promis_meta,
                studlab=paste(Cohort),
                comb.fixed = FALSE,
                comb.random = TRUE,
                hakn = FALSE,
                prediction=TRUE,
                sm="")
metaanalysis_promis

svg(file = 'promis_metaplot.svg') 
promis_metaplot <- forest(metaanalysis_promis,
       xlim = c(-1,1),
       col.diamond = "black",
       print.I2.ci = FALSE,
       xlab.pos = 0,
       overall.hetstat = TRUE, 
       print.I2	= TRUE,
       digits = 3,
       text.random = "Meta Analysis",
       leftcols = c("studlab", "effect", "ci", "n"), 
       leftlabs = c("Cohort", "Estimate","95%-CI", "N"),
       just = "center", just.addcols = "center", just.studlab = "center",
       rightcols = FALSE
)
dev.off()

```

```{r}

Pitt_pdds_covar_1115 <- lm(formula = pdds_median ~ age_latestPRO + sex + race_ethnicity_combo + age_firstsx + dx_dur_adjust + DMT_Group + PC1, data = Pitt_pdds_median_latest_dem_1115)
summary(Pitt_pdds_covar_1115)$coefficients
tab_model(Pitt_pdds_covar_1115)

CUIMC_pdds_covar_1115 <- lm(formula = pdds_median ~ age_latestPRO + sex + race_ethnicity_combo + age_firstsx + dx_dur_adjust + DMT_Group + PC1, data = CUIMC_pdds_median_latest_dem_1115)
summary(CUIMC_pdds_covar_1115)$coefficients
tab_model(CUIMC_pdds_covar_1115)

pdds_meta <- fread("meta_pdds.csv")

metaanalysis_pdds <- metagen(TE,
                seTE,
                data=pdds_meta,
                studlab=paste(cohort),
                comb.fixed = FALSE,
                comb.random = TRUE,
                hakn = FALSE,
                prediction=TRUE,
                sm="")
metaanalysis_pdds

svg(file = 'pdds_metaplot.svg') 
pdds_metaplot <- forest(metaanalysis_pdds,
       xlim = c(-1,1),
       col.diamond = "black",
       print.I2.ci = FALSE,
       xlab.pos = 0,
       overall.hetstat = TRUE, 
       print.I2	= FALSE,
       digits = 3,
       text.random = "Meta Analysis",
       leftcols = c("studlab", "effect", "ci", "n"), 
       leftlabs = c("Cohort", "Estimate","95%-CI", "N"),
       just = "center", just.addcols = "center", just.studlab = "center",
       rightcols = FALSE
)
dev.off()

```